---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yimiao Yuan
thanks: "Code and data are available at: https://github.com/YimiaoYuan09/Pet_Ownership_Impact"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(haven)
library(knitr)
library(arrow)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

## Data Source


## Features

```{r}
#| include: false
#| warning: false
#| message: false

# read in raw data
raw_pet_data <-  read_sav(here::here("data/raw_data/raw_data.sav"))
```

```{r}
#| label: tbl-raw
#| tbl-cap: "Preview of the raw pet owners and non-pet owners dataset"
#| message: false
#| echo: false

raw_pet_data[1:5, 1:8] |>
  kable()
raw_pet_data[1:5, 9:15] |>
  kable()
raw_pet_data[1:5, 16:19] |>
  kable()
```

## Methodology

```{r}
#| include: false
#| warning: false
#| message: false

# read in cleaned data
pet_data <-
  read_parquet(here::here("data/analysis_data/clean_pet_data.parquet"))
```

```{r}
#| include: false
#| warning: false
#| message: false

# change column type to factor
pet_data <-
  pet_data |>
  mutate(
    pet_group = factor(
      pet_group,
      levels = c(
        "non-pet owners", 
        "pet owners"
      )
    ),
    age_group = factor(
      age_group,
      levels = c(
        "less than 15 years",
        "15-25 years",
        "26-35 years",
        "36-45 years",
        "46-55 years",
        "greater than 56 years"
      )
    ),
    gender = factor(
      gender,
      levels = c(
        "male",
        "female"
      )
    ),
    bmi_status = factor(
      bmi_status,
      levels = c(
        "under weight",
        "normal weight",
        "over weight",
        "obese"
      )
    ),
    depression_status = factor(
      depression_status,
      levels = c(
        "depressed",
        "non-depressed"
      )
    ),
    pet_type = factor(
      pet_type,
      levels = c(
        "dog",
        "cat",
        "bird",
        "rabbit",
        "dog, cat",
        "dog, bird",
        "dog, cat, bird, rabbit",
        "cat, bird",
        "cat, bird, rabbit"
      )
    )
  ) |>
  select(pet_group, age_group, gender, bmi_status, depression_status, pet_type)
```

```{r}
#| label: tbl-clean-data
#| tbl-cap: "Preview of the cleaned pet owners and non-pet owners dataset"
#| message: false
#| echo: false

pet_data[1:5, 1:6] |>
  kable()
```

```{r}
#| label: tbl-summary
#| tbl-cap: "Statistics summary of the cleaned pet owners and non-pet owners dataset"
#| message: false
#| echo: false

pet_data |>
  summary() |>
  kable()
```


## Data Analysis
```{r}
#| label: fig-pet-type
#| fig-cap: The distribution of pet species
#| echo: false
#| warning: false
#| message: false
pet_data |>
  filter(pet_group == "pet owners") |>
  ggplot(aes(x = pet_type)) +
  coord_flip() +
  geom_bar(position = "dodge") +
  theme_minimal() +
  labs(
    x = "Type of pets",
    y = "Number of respondents"
  )
```

```{r}
#| label: fig-bmi
#| fig-cap: The relationship between BMI status and pet ownership by gender
#| echo: false
#| warning: false
#| message: false
pet_data |>
  ggplot(aes(x = bmi_status, fill = pet_group)) +
  geom_bar(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  labs(
    x = "BMI Status",
    y = "Number of respondents",
    fill = "Group"
  )+
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-depression
#| fig-cap: The relationship between depression status and pet ownership by age group
#| echo: false
#| warning: false
#| message: false
pet_data |>
  ggplot(aes(x = depression_status, fill = pet_group)) +
  geom_bar(position = "dodge") +
  facet_wrap(facets = vars(age_group)) +
  theme_minimal() +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  labs(
    x = "Depression status",
    y = "Number of respondents",
    fill = "Group"
  ) +
  theme(legend.position = "bottom")
```


# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

# plot(first_model, "trace")
# 
# plot(first_model, "rhat")
```



\newpage


# References


